Regional and Urban Economics

### 2023-02-19 Retail Agglomeration_abstract_introduction_theori_econometric_approach.qmd
Add files via upload

The study utilize a quantitative research approach, employing spacial explanatory data analysis techniques to determine the location decisions of firms.
Geographical data was collected from locations in Norway showing all dentists, central places, retail agglomeration and other points of interest such as the government regulated wine monopoly.
Combines with regional income data a spatial regression analyses was used to identify the factors influencing the location decisions of firms.

@@

>>>>

The study utilize a quantitative research approach, employing spacial explanatory data analysis techniques to determine the location decisions of firms.
Geographical data was collected from locations in Norway showing all dentists, central places, retail agglomeration and other points of interest such as the government regulated wine monopoly.
Combined with regional income data a spatial regression analyses was used to identify the factors influencing the location decisions of firms.

@@

The theoretical framework for this study draws on Marshall's agglomeration principles, which emphasize spatial aspects of economic growth.
Hotelling's game theory is used to explain spatial competition by location.
Furthermore, adding the hybrid model whereas firms compete both in location and price, with consumers having a transportation cost and firms producing differentiated products.
Alsonso's bid-rent model and gravitational models also provides insights into how dentists or other retailer makes location decisions in the context of regional growth.

The dental industry provides an interesting industry to study for this research because of its unique characteristics.
Dental practices require a high degree of specialization and expertise.
At the same time, they need to be easily accessible to consumers.
Shopping malls and central places offer a continent location for dental practices that said competition for prime locations can be intense and push some in to spatial monopoly.

The result of this study indicates that dentist's with the highest income are usually located in central places in big cities.
The findings are in line with already exciting theories especially supporting the gravitational models and agglomeration attributes.
?????? Proving a central location within large cities are the best location to maximize profit for Dental practices.
???
